Large-Scale Content-Based Matching of MIDI and Audio Files

### 2015-03-16 paper.tex
Finishing introduction and making skeleton

>>>>

Fortunately, the goal of matching MIDI and audio files is to find pairs which have \textit{content} in common (i.e., the MIDI file is a transcription of the audio file), an information source which is available regardless of metadata quality.
However, comparing content has the potential to require much more computation than a fuzzy text comparison, and $NM$ comparisons must be made to match a MIDI dataset of size $N$ to an audio file dataset of size $M$.
Motivated by this, we propose a system which can \textit{efficiently} match MIDI files to audio based solely on their content.
Our system learns to hash MIDI and audio content to a common hamming space where sequences of vectors can be compared efficiently using dynamic time warping (DTW).

In the following section, we detail the dataset of MIDI files we scraped from the Internet and describe how we prepared a subset for training our hasher.
Our cross-modality hashing model is then described in Section \ref{sec:hashing}.
In Section \ref{sec:dtw}, we cover our fast hash sequence DTW method and its accompanying pruning techniques.
Finally, we evaluate our system's performance on the task of matching files from our MIDI dataset to entries in the Million Song Dataset \cite{bertin2011million}.

\section{The MIDI Dataset}
\label{sec:dataset}

\section{Cross-Modality Hashing of MIDI and Audio Data}
\label{sec:hashing}

\section{Fast DTW Matching of Hash Sequences}
\label{sec:dtw}

\section{Matching MIDI Files to the MSD}
\label{sec:msd}
